\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-11-17 submission/manuscript.tex

Studies of unculturable microbes often combine methods based on DNA,
such as 16S rRNA sequencing and metagenomics, with methods that allow
insights into the metabolic status, such as metaproteomics. To apply
these techniques to the microbial community inhabiting the surfaces of
marine macrophytes it is advisable to perform a selective DNA and
protein isolation prior to the analysis to avoid biases due to the host
material being present in high quantities. Two protocols for DNA and
protein isolation were adapted for selective extractions of DNA and
proteins from epiphytic communities inhabiting the surfaces of two
marine macrophytes, the seagrass \emph{Cymodocea nodosa} and the
macroalga \emph{Caulerpa cylindracea}. Protocols showed an almost
complete removal of the epiphytic community regardless of the sampling
season, station, settlement or host species. The obtained DNA was
suitable for metagenomic and 16S rRNA sequencing, while isolated
proteins could be identified by mass spectrometry. The low presence of
host DNA and proteins in the samples indicated a high specificity of the
protocols. The procedures are based on universally available laboratory
chemicals making the protocols widely applicable. Taken together, the
adapted protocols ensure an almost complete removal of the macrophyte
epiphytic community. The procedures are selective for microbes
inhabiting macrophyte surfaces and provide DNA and proteins applicable
in 16S rRNA sequencing, metagenomics and metaproteomics.

>>>>

Studies of unculturable microbes often combine methods such as 16S rRNA
sequencing, metagenomics and metaproteomics. To apply these techniques
to the microbial community inhabiting the surfaces of marine macrophytes
it is advisable to perform a selective DNA and protein isolation prior
to the analysis to avoid biases due to the host material being present
in high quantities. Two protocols for DNA and protein isolation were
adapted for selective extractions of DNA and proteins from epiphytic
communities inhabiting the surfaces of two marine macrophytes, the
seagrass \emph{Cymodocea nodosa} and the macroalga \emph{Caulerpa
cylindracea}. Protocols showed an almost complete removal of the
epiphytic community regardless of the sampling season, station,
settlement or host species. The obtained DNA was suitable for
metagenomic and 16S rRNA sequencing, while isolated proteins could be
identified by mass spectrometry. Low presence of host DNA and proteins
in the samples indicated a high specificity of the protocols. The
procedures are based on universally available laboratory chemicals
making the protocols widely applicable. Taken together, the adapted
protocols ensure an almost complete removal of the macrophyte epiphytic
community. The procedures are selective for microbes inhabiting
macrophyte surfaces and provide DNA and proteins applicable in 16S rRNA
sequencing, metagenomics and metaproteomics.
